---
title: "Upload Data to Project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Upload Stationary Acoustic Data to Project}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


### After running all the below code:
Go to https://www.nabatmonitoring.org/ and click partner portal.  Login to your account
and proceed to the project that matches project_id (projects tab). Click on your project 
and navigate there.  Once inside the project page, click the 'Bulk Upload Status' tab
and view the data that this script just processed. If there are errors, make changes and
try again with either this R code or the Website.

### Note:
All of uploads through nabatr use the 'Full Metadata' option. To view more information,
go to your project, select the 'Upload Survey Data' button at the top, and click any of
the types to popup a box with more information.  (Capture records are currently 
unavailable through nabatr.  Go to Website to upload.)


### Get a token for NABat Database
```{r}
library(nabatr)
# Enter your NABat username here
username = 'NABat_Username'
token = get_nabat_gql_token(username)
token

# Note: if you leave run token = get_nabat_gql_token(),
#   it will prompt you for a username and then a password
```


### Get Project dataframe which contains all of your NABat projects in the NABat Database
```{r}
# Refresh token
token = get_refresh_token(token)
# Get your projects lookup table
project_df = get_projects(token)
# Display your projects lookup table
project_df
```

### Select a project id from project_df above
```{r}
### Change this value to the project ID you want to upload data to
project_id = 000
```

### Get User ID
```{r}
user_id = get_user_id_by_email(username, token)
```

### Set data_type, file_name, and file_path
```{r}
# Type of data to be uploading ex:
## 'bulk_sae' = Stationary Acoustic data
## 'bulk_mae' = Mobile Acoustic Data
## 'bulk_hib' = Hibernacula Colony Count Data
## 'bulk_mat' = Maternity Colony Count Data
## 'bulk_ee' = Emergence Count Data
data_type = 'bulk_sae'
# Name of file to be uploaded into NABat website
file_name = 'name_of_csv.csv'
# Location of file to be uploaded and processed into NABat Database/Website
## Don't end in "/"
## valid Ex: /users/johndoe/downloads/example.csv
file_path = '/users/johndoe/downloads/example.csv' 
```


### Get a Preview File to use as a template
```{r}
# Generates a template/preview of the file_path csv
template = get_upload_file_preview(file_path, token, data_type)
```

### Get presigned URL to upload data to
```{r}
# Get the presigned information
presigned_data = get_presigned_data(project_id, token)
# Extract values needed to upload and process file
presigned_url = presigned_data$presigned_url
asUUid = presigned_data$asUUid
```

### Upload file to presigned URL
```{r}
# Pushes file into an s3 bucket in AWS
upload_res = upload_csv(presigned_url, file_path)
# Status code of 200 = Success
upload_res$status_code
```

### Process the file into the NABat database
```{r}
# Process file into the Database and uploads it into 
## the Website User interface under Bulk Upload Status
## and Acoustic Data
process_uploaded_csv(user_id, 
                     project_id, 
                     asUUid, 
                     template, 
                     file_name, 
                     token, 
                     data_type)
```















