---
title: "Build Stationary Acoustic Report"
output:
  html_document: default
---

## Extract Stationary Acoustic Data and Build a Report


### Get a token for NABat Database
```{r}
library(nabatr)
# Enter your NABat username here
username = 'NABat_Username'
token = get_nabat_gql_token(username)
token

# Note: if you leave run token = get_nabat_gql_token(),
#   it will prompt you for a username and then a password
```


### Get Project dataframe which contains all of your NABat projects in the NABat Database
```{r}
# Refresh token
token = get_refresh_token(token)
# Get your projects lookup table
project_df = get_projects(token)
# Display your projects lookup table
project_df
```


### Get all Stationary Acoustic Surveys within a single Project set with project_id
```{r}
# Refresh token
token = get_refresh_token(token)
# Fill in project id using the project_df lookup table
project_id = 000 # Set equal to one of your project ids

# Get survey dataframe 
sa_survey_df = get_sa_project_summary(token, 
                                      project_df, 
                                      project_id)
                                          
sa_proj_dates = unique(sa_survey_df$year)
# Display survey dataframe
sa_survey_df
```


### Get all Stationary Acoustic Survey wav file data.  Format: Stationary Acoustic Bulk Upload Template
```{r}
# Select Year for project (defaults to 1st available year)
year = sa_proj_dates[1]

# Refresh token
token = get_refresh_token(token)
# Get stationary acoustic bulk upload format dataframe
sa_bulk_df = get_sa_bulk_wavs(token, 
                               sa_survey_df,
                               year)
# Display stationary acoustic bulk upload format dataframe
sa_bulk_df
```


### Get Stationary Acoustic dataframe broken up into nightly observed data and get species_df
```{r}
token = get_refresh_token(token)
species_df = get_species(token)
# Get Acoustic stationary acoustic bulk dataframe
nightly_observed_list = get_observed_nights(sa_bulk_df)
```


### Build a Stationary Acoustic Report
```{r}
# Edit these two variables below to your local system (file_name, out_dir)
file_name = 'name_of_sa_report.docx'  
out_dir   = '/directory/to/download/report' # Make sure this ends without a '/'

sa_doc = build_sa_doc(out_dir = out_dir,
            project_df = project_df,
            project_id = project_id,
            sa_bulk_df = sa_bulk_df,
            sa_survey_df = sa_survey_df,
            species_df = species_df,
            selected_year = year,
            nightly_observed_list = nightly_observed_list,
            range_maps = TRUE)

# Save out your report
print(sa_doc, target = paste0(out_dir, '/', file_name))
```


