---
title: "Get Nightly Data"
output:
  html_document: default
---

## Extract Nightly data from NABat Project and convert to 'detection history' format

### Note: if you can't get nabatr to load on your computer, you can download this
###  data from the website by going to your projects, selecting a project, going
###  to the 'expore project data' button in the top right, selecting 'Frequency by
###  Time' tab at the top right and then clicking the 'Export NABat Data' button.
###  Skip to line 51


```{r}
library(nabatr)
# Enter your NABat username here
username = 'nabat_username'
token = get_nabat_gql_token(username = username)
token

# Note: if you leave run token = get_nabat_gql_token(),
#   it will prompt you for a username and then a password
```

### Pull Nightly Stationary acoustic data for 1 species
```{r}
# Refresh login token
token = get_refresh_token(token)

# Use get_nightly_data with minimum parameters
sae_nightly_data = get_nightly_data(token, 
  sp_code = 'MYLU',
  survey_type = 'bulk_sae') # Or bulk_mae or bulk_cc

# Display data
sae_nightly_data
```

### Use more variables to get more specific data
```{r}
# Refresh login token
token = get_refresh_token(token)

# Use get_nightly_data with all parameters
sae_nightly_data = get_nightly_data(token, 
  sp_code = c('MYLU', 'ANPA'), 
  sample_frame = c('CONUS','Alaska'),
  project_id = c(33,284),
  years = c(2015,2016,2017),
  survey_type = 'bulk_sae')

# Display data
sae_nightly_data
```
