---
title: "Get acoustic stationary NABat Data and Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get acoustic stationary NABat Data}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---




### Get a Graphical QL (GQL) token for NABat Database
```{r}
#library(nabatr)
devtools::load_all(".")
library(tidyverse)
library(lubridate)
# Enter your NABat username here
username_ = 'Tina Cheng'
token_ = get_nabat_gql_token(username = username_)
token_

# If you are not using R-Studio or are not prompted for a password use this code below
#  to manually add in your password with the password variable:
# token_ = get_nabat_gql_token(username = username_, password = 'your-password')
```

### Get Project dataframe which contains all of your acoustic stationary projects in the NABat Database
```{r}
# Get your projects lookup table
project_df_ = get_projects(token = token_)
# Display your projects lookup table
project_df_

```

### Get Species dataframe which contains a species lookup table for auto and manual ids
```{r}
# Get your species lookup table
species_df_ = get_species(token = token_)
# Display your species lookup table
species_df_

```

### Get all Acoustic Stationary Surveys within a single Project set with project_id_
```{r}
# Fill in project id using the project_df_ lookup table
project_id_ = 275 # Set equal to one of your project ids

# Get survey dataframe 
survey_df_ = get_project_surveys(token      = token_,
                                 project_df = project_df_,
                                 project_id = project_id_)
# Display survey dataframe
survey_df_
```

### Get all Acoustic Stationary Survey wav file data.  Format: Acoustic Stationary Bulk Upload Template
```{r}
colony_bulk_df_ = get_colony_bulk_counts(token = token_,
                                         survey_df = survey_df_,
                                         project_id = project_id_)

colony_bulk_df_
```

### Use the Acoustic Stationary acoustic bulk dataframe to build a dataframe for auto and manual species id data
```{r}
# Get Acoustic stationary acoustic bulk dataframe
nightly_observed_list_ = get_observed_nights(acoustic_bulk_df_)

auto_nights_df_ = nightly_observed_list_$auto_nightly_df
manual_nights_df_  = nightly_observed_list_$manual_nightly_df
  
# Display the two dataframes
manual_nights_df_
auto_nights_df_
```

### Extracting unique species found for manual and automatic nights acoustic data in long format
```{r}
# Individual species totals for either Manual or Automatic
manual_species_totals_l_ = get_species_counts_long(manual_nights_df_, filter=TRUE)
auto_species_totals_l_   = get_species_counts_long(auto_nights_df_, filter=TRUE)

# Both Manual and Automatic species totals 
all_species_totals_l_l_ = get_all_species_counts_long(auto_nights_df_, manual_nights_df_, fil = TRUE)
```

### Extracting unique species found for manual and automatic nights acoustic data in WIDE format
```{r}
# Extract totals from project at GRTS cell id and GRTS site name

# MANUAL
manual_species_totals_w_   = get_species_counts_wide(manual_nights_df_)
# --- totals at sites
manual_species_sites_df_w_ = manual_species_totals_w_$species_site_id_df
# --- totals at GRTS cell id
manual_species_grts_df_w_  = manual_species_totals_w_$species_grts_df

# AUTOMATIC
auto_species_totals_w_   = get_species_counts_wide(auto_nights_df_)
# --- totals at sites
auto_species_sites_df_w_ = auto_species_totals_w_$species_site_id_df
# --- totals at GRTS cell id
auto_species_grts_df_w_  = auto_species_totals_w_$species_grts_df

```

### Setup a leaflet map to show 
```{r}
grts_map = get_grts_leaflet_map(all_grts       = unique(survey_df_$grts_cell_id),
                                grts_with_data = unique(auto_nights_df_$GRTS))
# Display the grts map
grts_map
```

### Build Acoustic stationary .docx report
```{r}
# Edit This file path to your own output directory to store the report (No trailing '/')
out_dir_doc = here::here()
# Build report and return the doc to then save out
doc_ = build_col_doc(out_dir = out_dir_doc,
                    file_name  = paste0('doc_report_','_',Sys.Date(),'.docx'),
                    project_df = project_df_,
                    project_id = project_id_,
                    cover_photo = "/inst/templates/nabat_logo.png",
                    colony_bulk_df = colony_bulk_df_,
                    date = format(Sys.time(), "%B %d, %Y"))

# Save it out to a local directory
print(doc_, target = paste0(out_dir_doc, '/', paste0('colony_count_report_',project_id_,'_',format(Sys.time(), '%Y_%m_%d_%H%M%S'),'.docx')))
```

### Build Acoustic stationary HTML report
```
# Edit This file path to your own output directory to store the report (No trailing '/')
out_dir_html = '/path/to/output/directory'

# Build Report and save out the report
get_acoustic_stationary_report(token      = token_,
                               output_dir = out_dir_html,
                               file_name  = paste0('report_',project_id_,'_',Sys.Date(),'','.html'),
                               nightly_plots_type = 'sites', # 'grts' | 'sites'
                               output_type = 'html',
                               project_id = project_id_,
                               survey_df = survey_df_,
                               acoustic_bulk_df = acoustic_bulk_df_,
                               nightly_observed_list = nightly_observed_list_,
                               num_plots = 20)
```



