---
title: "Get_Acoustic_Data"
output:
  html_document: default
---

### Explore your stationary acoustic NABat data using this Rmd example


First, let's download these packages
```{r}
# Install devtools
if(!require(devtools)){install.packages('devtools')}

# Install ghql and nabatr packages using devtools
devtools::install_github("ropensci/ghql")
devtools::install_github("talbertc-usgs/nabatr")
library(nabatr)
```

Get a Graphical QL token for NABat Database
```{r}
# Enter your NABat username here
username_ = 'NABat_Username'
token_ = get_nabat_gql_token(username = username_)
# If you are not using R-Studio and are not prompted for a password use this code below
#  to manually add in your password with the password variable:
# token_ = get_nabat_gql_token(username = username_, password = 'your-password')
```

Get Project dataframe which contains all of your acoustic stationary 
  projects in the NABat Database
```{r}
# Get your projects lookup table
project_df_ = nabatr::get_projects(token    = token_, 
                                  username = username_)
# Display your projects lookup table
project_df_
```

Get all Acoustic Stationary Surveys within a single Project set with project_id_
```{r}
# Fill in project id using the project_df_ lookup table
project_id_ = 283

# Get survey dataframe 
survey_df_ = nabatr::get_project_surveys(username   = username_,
                                        token      = token_,
                                        project_id = project_id_)
# Display survey dataframe
survey_df_
```

Get all Acoustic Stationary Survey wav file data.  Format: Acoustic Stationary Bulk Upload Template
```{r}
# Get stationary acoustic bulk upload format dataframe
acoustic_bulk_df_ = nabatr::get_acoustic_bulk_wavs(token      = token_, 
                                                   username   = username_, 
                                                   survey_df  = survey_df_,
                                                   project_id = project_id_)
# Display stationary acoustic bulk upload format dataframe
acoustic_bulk_df_
```

Use the Acoustic Stationary acoustic bulk dataframe to build a dataframe for auto and manual species id data
```{r}
# Get Acoustic stationary acoustic bulk dataframe
nightly_observed_list = nabatr::get_observed_nights(acoustic_bulk_df_)

manual_nights_df_ = nightly_observed_list$auto_nightly_df
auto_nights_df_   = nightly_observed_list$manual_nightly_df
  
# Display the two dataframes
manual_nights_df_
auto_nights_df_
```

Setup a leaflet map to show 
```{r}
grts_map = get_grts_leaflet_map(project_id     = project_id_,
                                all_grts       = unique(survey_df_$grts_cell_id),
                                grts_with_data = unique(auto_nights_df_$GRTS))
# Display the grts map
grts_map
```

build report
```{r}
get_acoustic_stationary_report(token      = token_,
                               username   = username_,
                               output_dir = '/Users/kenns/Downloads',
                               file_name  = 'report123.html',
                               project_id = project_id_)

```








