---
title: "Get_Acoustic_Data"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

### Explore your stationary acoustic NABat data using this Rmd example

Download, this package
```{r}
if(!require(devtools)){install.packages(devtools)}
devtools::install_github("talbertc-usgs/nabatr")
library(nabatr)
```

Get a Graphical QL token for NABat Database
```{r}
username_ = 'NABat_Username'
token_ = get_nabat_gql_token(username = username_)
# If not using R-Studio and you aren't prompted for a password use this:
# token_ = get_nabat_gql_token(username = username_, password = 'your-password')
```

Get Project dataframe which contains all of your acoustic stationary 
  projects in the NABat Database
```{r}
project_df_ = nabatr::get_projects(token    = token_, 
                                  username = username_)
project_df_
```

Get all Acoustic Stationary Surveys within a single Project set with project_id_
```{r}
project_id_ = 'project_id from project_df'
survey_df_ = nabatr::get_project_surveys(username   = username_,
                                        token      = token_,
                                        project_id = project_id_)
survey_df_
```

Get all Acoustic Stationary Survey wav file data.  Format: Acoustic Stationary Bulk Upload Template
```{r}
acoustic_bulk_ = nabatr::get_acoustic_bulk_(token      = token_, 
                                                username   = username_, 
                                                survey_df  = survey_df_,
                                                project_id = project_id_)
acoustic_bulk_
```
